Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-02-24 ccppabc/text/main.tex
more updates

In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
accounts for sample variance. In principle, they also have the advantage that they can account for 
sources of systematic uncertainties in the observational data.

>>>>

{\bf \color{red} Overall, the constraints from ABC-PMC are consistent with those from 
the Gaussian pseudo-likelihood MCMC method; however, using ABC-PMC has a number of 
advantages. ABC-PMC utilizes a forward generative model. Our forward generative model, 
for instance, accounts for sample variance. In principle, they also have the advantage that they can account for sources of systematic uncertainties in the observational data. 
}

%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.
